Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-21 talk/iwtc11/paper.tex
expand related work somewhat

\end{tabular}
}
\end{center}
\label{fig:benchmarks}
\caption{XXX}
\end{figure*}

@@

All the optimizations presented here are completely standard \cite{XXX} [dragon
book or similar].

LuaJIT does the same

SPUR does all these optimizations manually, moves allocations out of loop but
does not explode objects

>>>>

\end{tabular}
}
\end{center}
\label{fig:benchmarks}
\caption{Benchmark Results in Seconds}
\end{figure*}

@@

All the optimizations presented here are completely standard
\cite{muchnick_advanced_1997}. XXX

Mike Pall, the author of LuaJIT\footnote{\texttt{http://luajit.org/}} seems to
have developped the described technique independently. There are no papers about
LuaJIT but the author of it writes on a mailing list: "The LOOP pass does
synthetic unrolling of the recorded IR, combining copy-substitution with
redundancy elimination to achieve code hoisting. The unrolled and
copy-substituted instructions are simply fed back into the compiler pipeline,
which allows reuse of all optimizations for redundancy elimination. Loop
recurrences are detected on-the-fly and a minimized set of PHIs is generated."
\cite{pall_luajit_2009}

SPUR \cite{bebenita_spur:_2010} implements loop-invariant code motion
directly, by explicitly marking as loop-invariant all variables that stay the
same along all looping paths and then moving all pure computation that depends
only on these variables out of the loop. SPUR can also hoist loads out of the
loop if nothing in the loop can ever write to the memory location. It can also
move allocations out of the loop, but does not replace the object by its fields.
This saves only the allocation, not the access to the object fields.
